UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-16 paper/paper.tex
paper updates

\begin{algorithm}[h]
\caption{test}
\label{alg:squeeze-them-in}
 \KwData{Cluster averages for CPU and memory, List of machines from Threshold Based Report, List of other machines}
 \KwResult{List of machines that can be powered down}
 \algrenewcommand\algorithmicfunction{\textbf{class}}
 \algrenewcommand\algorithmicprocedure{\textbf{method}}
 %\begin{algorithmic}[1]

  %$float spare_cpu;$
  %$float spare_memory;$

 %  \ForAll{machine in Other Machines} {
%        \If{$machine.cpu \geq cluster.cpu$} {
%        \If{a}
 %              \State test % spare_cpu  cluster.cpu  machine.cpu
 %        \EndIf
%        \If{machine.memory < cluster.memory} {
%                spare_memory += cluster.memory - machine.memory
%        }
 %  }
\ForAll{machine in otherMachines}{
        \If{$machine.cpu < cluster.cpu$} {
                 $spareCpu += clusterCpu - machineCpu$
        }
        \If{$machine.memory < cluster.memory$}{
        	$spareMemory += clusterMemory - machineMemory$
        }
        %\EndIf
}
%\EndFor
% \end{algorithmic}
\end{algorithm}

Computation: Calculate spare capacity based on average CPU and memory usage. Iterate through a pool of available machines (not included in input report) and advertise available capacity only if CPU and memory usage is lower than average. Aggregate spare capacity results.

Output: List of machines that can be shutdown based on computed spare-capacity.

@@

>>>>

\begin{algorithm}[h]
\caption{Squeeze them in suggestion strategy}
\label{alg:squeeze-them-in}
 \KwData{Cluster averages for CPU and memory, List of machines from Threshold Based Report, List of other machines}
 \KwResult{List of machines that can be powered down}
 \algrenewcommand\algorithmicfunction{\textbf{class}}
 \algrenewcommand\algorithmicprocedure{\textbf{method}}

  $float spareCpu = 0;$
  $float spareMemory = 0;$
  $ID[ ] machinesToExclude;$

\ForAll{machine in otherMachines}{
        \If{$machine.cpu < cluster.cpu$} {
                 $spareCpu += clusterCpu - machineCpu$
        }
        \If{$machine.memory < cluster.memory$}{
        	$spareMemory += clusterMemory - machineMemory$
        }
}

\ForAll{machine in machinesFromReport}{
        \If{$(spareCpu - machine.cpu > 0) \&\& (spareMemory - machine.memory > 0)$}{
                add machine to machinesToExclude;
        }
}

\Return machinesToExclude;

\end{algorithm}

@@

\begin{algorithm}[h]
\caption{New configuration suggestion}
\label{alg:new_configuration}
 \KwData{List of machines from Threshold Based Report, List of available schemes;}
 \KwResult{List of machines that can be powered down}
 \algrenewcommand\algorithmicfunction{\textbf{class}}
 \algrenewcommand\algorithmicprocedure{\textbf{method}}

  $float spareCpu = 0;$
  $float spareMemory = 0;$
  $ID[ ] machinesToExclude;$

\ForAll{machine in otherMachines}{
        \If{$machine.cpu < cluster.cpu$} {
                 $spareCpu += clusterCpu - machineCpu$
        }
        \If{$machine.memory < cluster.memory$}{
                $spareMemory += clusterMemory - machineMemory$
        }
}

\ForAll{machine in machinesFromReport}{
        \If{$(spareCpu - machine.cpu > 0) \&\& (spareMemory - machine.memory > 0)$}{
                add machine to machinesToExclude;
        }
}

\Return machinesToExclude;

\end{algorithm}
